Essays in Computational Management Science

### 2018-05-10 Chapters/Chapter01.tex
Hathor: more results in Hathor's analysis.

When a new transaction is added to the Hathor's network, it uses a depth-first search \citep{cormen2009introduction} to update the aggregated weight of the directly and indirectly confirmed transactions. The depth-first search is interrupted when it reaches a transaction which the accumulated weight is larger than a given threshold. This interruption significantly increases the overall performance of the simulation. If the accumulated weight is an important metric, the whole network may be updated in specific times to get a measurement (instead of every new transaction).

@@

@@

@@

Finally, even with both blocks and transactions, Hathor's blocks are similar to Bitcoin's blocks, and they share the same math. To confirm that, see Figure {fig:hathor-tbb}, where the red curve is Bitcoin's distribution of time between blocks and the blue histogram is Hathor's time between blocks. I also made several tests adding and removing miners to check the difficulty adjustment and it worked properly.

@@

>>>>

When a new transaction is added to the Hathor's network, it uses a depth-first search \citep{cormen2009introduction} to update the aggregated weight of the directly and indirectly confirmed transactions. The depth-first search is interrupted when it reaches a transaction which the accumulated weight is larger than a given threshold. This interruption significantly increases the overall performance of the simulation. If the accumulated weight of the whole DAG is an important metric, the whole DAG may be updated in specific times to get a measurement (instead of every new transaction).

@@

It is also possible to create metrics, which sample a statistic every $\Delta t$ seconds. There are two metrics available: (i) TipsMetric, which stores the number of tips at a given simulation time, and (ii) UtterlyAcceptanceMetric, which finds the new utterly accepted transactions and store how long it took.

To find the network validated transactions, I run a breadth-first search (bfs) for each tip. Transactions visited in all searches are being confirmed by all tips and, by definition, are network validated transactions.

@@

\section{Confirmation time}

@@

Finally, even with both blocks and transactions, Hathor's blocks are similar to Bitcoin's blocks, and they share the same math. To confirm that, see Figure \ref{fig:hathor-tbb}, where the red curve is Bitcoin's distribution of time between blocks and the blue histogram is Hathor's time between blocks. I also made several tests adding and removing miners to check the difficulty adjustment and it worked properly.

@@

\section{Load changing}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{./images01/new/many-loadings.pdf}

\caption{DAG visualization when the loading is changed over time. \label{fig:hathor-load-changing}}
\end{figure}

\section{Number of tips}

\begin{figure}[!htb]
\centering
\subfloat[Only low load scenarios]{\includegraphics[width=\textwidth]{./images01/new2/tips_aggregate2.png}}

\subfloat[All load scenarios]{\includegraphics[width=\textwidth]{./images01/new2/tips_aggregate.png}}

\caption{Histogram of the number of tips for different load scenarios. As expected, the number of tips increases with $\lambda_\text{TX}$. \label{fig:hathor-tips}}
\end{figure}

\section{Network validated transactions}

\begin{figure}[!htb]
\centering
\subfloat[Only low load scenarios]{\includegraphics[width=\textwidth]{./images01/new2/nv_low.png}}

\subfloat[All load scenarios]{\includegraphics[width=\textwidth]{./images01/new2/nv_all.png}}

\caption{Histogram of the time it takes for a transaction to be network validated. \label{fig:hathor-tips}}
\end{figure}

\section{Transaction's classification}

### 2018-05-10 Chapters/hathor-architecture.tex
Hathor: more results in Hathor's analysis.

@@

%\section{Attacks \& Conflicting transactions}
%\section{Scripts \& Contracts}

>>>>

Another transaction classification concerns its validation by the network. A transaction is said to be network validated if there are confirming paths from all tips to the transactions, i.e., the whole network has validated that the transaction is valid. It is important to notice that a transaction may be network validated but still pending, or even be confirmed but not network validated.

@@

%\section{Attacks \& Conflicting transactions}
%\section{Scripts \& Contracts}
%\section{Bandwidth consumption}
